QCL: Added value of differential correlation

### 2012-02-06 inst/doc/article.Rnw
Fixed R CMD build and check

\begin{figure}[ht]
  \centerline{\includegraphics[height=7cm]{qcl.pdf}}
  \vspace{-15pt}
  \caption{{\scriptsize QCL mapping: We start by looking at a single genetic marker and dividing our populaiton into two groups.
  We start by choosing a phenotype (red), and use its expression to detect the red module (high correlation in gray genotype). 
  We see that something underlying our current marker in the gray genotype regulates the expression of red (but not blue)}}
  \vspace{-20pt}
  \label{fig:qcl}
\end{figure}

\begin{figure}[ht]
  \centerline{\includegraphics[height=6cm]{qcl_n.pdf}}
  \vspace{-15pt}
  \caption{{\scriptsize Reconstructed pathway location from gene expression data: Insight into the underlying (hidden) regulatory network 
  can be obtained when we look at the amount of expression showing the same switch. Depending on the amount of blue expressions 
  co-affected we can guestimate the location of the red expression inside the pathway}}
  \vspace{-20pt}
  \label{fig:qcl_n}
\end{figure}

>>>>

%\begin{figure}[ht]
%  \centerline{\includegraphics[height=7cm]{qcl.pdf}}
%  \vspace{-15pt}
%  \caption{{\scriptsize QCL mapping: We start by looking at a single genetic marker and dividing our populaiton into two groups.
%  We start by choosing a phenotype (red), and use its expression to detect the red module (high correlation in gray genotype). 
%  We see that something underlying our current marker in the gray genotype regulates the expression of red (but not blue)}}
%  \vspace{-20pt}
%  \label{fig:qcl}
%\end{figure}

%\begin{figure}[ht]
%  \centerline{\includegraphics[height=6cm]{qcl_n.pdf}}
%  \vspace{-15pt}
%  \caption{{\scriptsize Reconstructed pathway location from gene expression data: Insight into the underlying (hidden) regulatory network 
%  can be obtained when we look at the amount of expression showing the same switch. Depending on the amount of blue expressions 
%  co-affected we can guestimate the location of the red expression inside the pathway}}
%  \vspace{-20pt}
%  \label{fig:qcl_n}
%\end{figure}
